---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DutchWeather

```{r, echo = FALSE, results='asis'}
cat(
	badger::badge_devel("Glender/DutchWeather", "purple"),
	badger::badge_codefactor("rossellhayes/ipa"),
	badger::badge_lifecycle("maturing", "blue"),
	badger::badge_github_actions("rossellhayes/ipa"),
	badger::badge_codecov("rcannood/princurve"),
	badger::badge_code_size("Glender/DutchWeather")
)
```

The goal of DutchWeather is to provide easy to use functions to download weather statistics from the KNMI website.

## :arrow_double_down: Installation

Assuming the devtools package is installed correctly, you can install the development version of DutchWeather with:

``` r
# install.packages("devtools")
devtools::install_github("Glender/DutchWeather")
```
## :sunny: :umbrella: :cloud: :eyeglasses: Example

Suppose you want to download some daily weahter statistics for research purposes:

```{r example}
library(DutchWeather)
## get daily weather data from the KNMI website
data <- get_daily_zipdata(station_id = 260)

# show bottem rows
tail(data)

```

## :speech_balloon: Help

The documentation of all functions can be accessed by `?<function-name>` or navigate via the package documentation help page `?DutchDayDummies`.
```
# For example:
?get_daily_zipdata
```


